\bf Faster Neural Machine Translation Inference

### 2018-01-23 fast-beam/fast-beam.tex
fast nmt paper

We shall leave the matrix multiplication for the next proposal and future work, and concentrate on the last three steps. There are algorithmic similarites between these steps, which we outline in ???.

??? alogirthm of each step

>>>>

We shall leave the matrix multiplication for the next proposal and future work, and concentrate on the last three steps, the outline of which are shown in ???.
